%-------------------------
% Resume in Latex
% Author : Aditya Saini
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNH}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListStartBullets}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

\begin{tabular*}{\textwidth}{L@{\extracolsep{\fill}}C@{\extracolsep{\fill}}R}
  \href{mailto:saini91@purdue.edu}{saini91@purdue.edu} &
  \multirow{2}{*}{\Huge \textbf{Aditya Saini}} &
  \href{https://sunnyv.surge.sh}{sunnyv.surge.sh} \\
  (908) 912-6974 & & US Citizen
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{West Lafayette, IN}
      {B.S. in Computer Science and Mathematics}{Expected May 2029}
      \resumeItemListStart
        \resumeItem{Concentration}{Machine Intelligence}
        \resumeItem{Coursework}{Data Structures \& Algorithms, Systems Programming, Linear Algebra, Multivariable Calculus, Physics (Mechanics \& E\&M), Object-Oriented Programming, Discrete Math, Probability}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Experience \& Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Natural Language Shell (NLSH)}{Remote}
      {Creator \& Software Engineer}{July 2025 -- Present}
      \resumeItemListStart
        \resumeItemNH{Designed and implemented a lightweight command-line shell written in C that executes commands based on natural language input.}
        \resumeItemNH{Developed custom tokenization, basic intent parsing, and bash command mapping for user-friendly interaction.}
        \resumeItemNH{Built setup tooling with `setup.sh` for cross-platform installation; documented architecture on GitHub.}
        \resumeItemNH{Exploring futher integration with DeepSeek R1 / OpenAI's API  to support more complex queries.}
      \resumeItemListEnd

    \resumeSubheading
      {Personal Website/Portfolio}{Remote}
      {Developer \& Designer}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItemNH{Designed and developed a personal portfolio website using HTML, CSS, and JavaScript to showcase projects in systems programming, robotics, and music.}
        \resumeItemNH{Implemented responsive design principles for cross-device compatibility and optimized performance.}
        \resumeItemNH{Deployed the site using Surge for fast, static hosting with a custom domain.}
      \resumeItemListEnd

    \resumeSubheading
      {FIRST Robotics Competition Team 2554}{Edison, NJ}
      {Build President \& Programming Captain}{Sep 2021 -- June 2025}
      \resumeItemListStart
        \resumeItemNH{Mentored new programmers and coordinated between mechanical, electrical, and software subteams.}
        \resumeItemNH{Led software development for autonomous systems, creating the highest scoring routine at District Championships.}
        \resumeItemNH{Acted as a communication bridge between programming and build teams, translating software requirements into actionable hardware adjustments.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd

\section{Selected Technial Projects}
  \resumeSubHeadingListStartBullets
    \resumeSubItem{HawkVision (FRC 2023)}
      {A computer vision pipeline using OpenCV in Java to detect and differentiate scoring objects. Integrated into autonomous routines with PID control.}
    \resumeSubItem{Arduino Synthesizer (Physics Project)}
      {Built a simple synthesizer using Arduino to demonstrate waveform generation and audio signal manipulation for AP Physics.}
  \resumeSubHeadingListEnd

\section{Involvement}
  \resumeSubHeadingListStartBullets
    \resumeSubItem{Hindi USA Volunteer Teacher}
      {Taught conversational Hindi and grammar through interactive games and activities; fostered a supportive learning environment.}
    \resumeSubItem{Kumon Math Instructor}
      {Taught advanced math (pre-calc to calc 2) to K-12 students, focused on building logical reasoning and strong foundations.}
  \resumeSubHeadingListEnd

\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {C, C++, Python, Java, JavaScript, Bash, HTML/CSS, LaTeX}
    \resumeSubItem{Technologies}
      {Git, OpenCV, React, Node.js, Flask, SQL, Arduino, Linux, VS Code}
    \resumeSubItem{AI Tools}
      {Claude, Cursor, Copilot, Gemini CLI, ChatGPT}
  \resumeSubHeadingListEnd

\end{document}